%====================
% EXPERIENCIA A
%====================

\subsection{{Data Scientist  \hfill June 2024 --- Present}}
\subtext{Accenture \hfill Santiago, Chile}
\begin{zitemize}
\item Developed and deployed end-to-end predictive solutions for one of the largest pulp companies worldwide, ranked in Forbes Global 2000's 2023 list (under NDA due to confidentiality agreements). The solutions focused on optimizing industrial processes using AI.
\item Worked extensively with Python, PyTorch, TensorFlow for model development, and integrated solutions using Google Cloud Platform (GCP) services such as Google Cloud Storage (GCS), BigQuery, Vertex AI, Cloud Scheduler, Cloud Functions, and APIs.
\item Leveraged Infrastructure as Code (IaC) principles using Terraform to manage GCP resources, ensuring efficient and scalable deployments of data pipelines and machine learning models.
\item Collaborated with cross-functional teams to design, develop and implement predictive models aimed at optimizing chemical processes and production efficiency.
\item GenAI: Multimodal RAG, Chatbots and other applications using LangChain and LangGraph.
\item Courses; GenAI Specialist (Basic), Getting Started with Responsible AI.
\end{zitemize}

%====================
% EXPERIENCIA B
%====================
\subsection{{Data Scientist  \hfill July 2023 --- May 2024}}
\subtext{ISAtech \hfill Santiago, Chile}
\begin{zitemize}
\item Developed neural network-based models to support remote ECG diagnostics, addressing critical healthcare shortages in specific regions.
\item Contributed to the development of a model for acceptance/rejection of ECG readings and anomaly detection to prioritize high-risk cases.
\item Implemented an algorithm using computer vision techniques on ECG spectrograms to detect acute myocardial infarction (AMI), with an accuracy of 94\%. 
\item Demonstrated the technology at national health conferences, including Congreso Futuro.
\item Technical Stack: Python 3, PyTorch 2, PyTorch Lightning, Tensorboard, GIT, local server computation.
\item Contact: Paul Lieutier, Lead AI \hfill paul.lieutier@free.fr
\end{zitemize}

%====================
% EXPERIENCIA C
%====================
\subsection{{Freelance Data Analyst \hfill August 2022 --- June 2023}}
\subtext{FoxIntelligence \hfill Paris, France (Remote)}
\begin{zitemize}
\item Conducted 7 data analysis missions for various e-commerce categories, identifying classification issues and proposing solutions based on text pattern detection using REGEX.
\item Improved product classification accuracy to 100\% for major retailers such as Amazon, eBay, and Zalando in categories including Alcoholic Beverages, Homecare, Cosmetics, and Nutrition.
\item Technical Stack: Tableau, REGEX.
\item Contact: Alexandre Sena, Senior Data Analyst \hfill alexandre.sena@foxintelligence.fr
\end{zitemize}

%====================
% EXPERIENCIA D
%====================
\subsection{{Robotics Engineer Internship \hfill July 2021 --- January 2022}}
\subtext{Solystic \hfill Paris, France}
\begin{zitemize}
\item Developed an autonomous human-following robot using LIDAR and computer vision for detecting color-coded safety vests worn by operators.
\item Integrated LIDAR sensors for distance measurement and cameras for visual tracking, achieving a robust multi-sensor fusion system for precise human tracking.
\item The tracking algorithm was validated and tested in real-world scenarios, receiving approval from the executive board.
\item Technical Stack: Python 3, C, QtCreator, motion planning, tracking algorithms.
\item Contact: Hicham El Bernoussi, Lead Computer Vision & AI \hfill hicham.el-bernoussi@solystic.com
\end{zitemize}
