\subsection{{Data Scientist \hfill June 2024 --- Present}}
\subtext{Accenture \hfill Santiago, Chile}
\begin{zitemize}
\item Designed and deployed \textbf{AI-based predictive models} for a global pulp company using advanced \textbf{time series forecasting architectures} such as \textbf{LSTM}, \textbf{TSMixer}, and \textbf{PatchTST}, achieving a projected \textbf{\$0.7M USD/year} in chemical savings. Models were integrated into production and PI Vision for real-time monitoring.
\item Developed an end-to-end \textbf{recommendation system} for one of Chile’s top beverage companies to optimize workforce allocation (pickers, forklift drivers, consolidators), delivering an estimated \textbf{\$5M USD/year} in savings.
\item Delivered a \textbf{computer vision solution} for a leading mining and chemical company to audit nitrate loading and wait times, enabling a \textbf{\$1.2M USD/year} business case through automated anomaly detection and visual audit tools.
\item Explored and prototyped \textbf{Generative AI applications}, including \textbf{multimodal RAG}, AI assistants, and chatbot interfaces using \textbf{LangChain} and \textbf{LangGraph}.
\item Technical stack: \textbf{Python, PyTorch, TensorFlow, Terraform}; Google Cloud Platform services such as \textbf{BigQuery, Vertex AI, Cloud Functions, Cloud Scheduler, Cloud Storage (GCS)}.
\end{zitemize}

\subsection{{Data Scientist / ISAtech \hfill July 2023 --- May 2024}}
\subtext{PSINet \hfill Santiago, Chile}
\begin{zitemize}
\item Co-developed an \textbf{AI-powered ECG diagnostic system} to support remote triage in underserved regions, including \textbf{Acceptance/Rejection models} and a \textbf{Myocardial Infarction (MI)} detection algorithm using \textbf{computer vision on ECG spectrograms}, achieving \textbf{94\% accuracy} on production data.
\item Designed a \textbf{U-Net architecture} for dense segmentation of time series.
\item Technical stack: \textbf{Python 3, PyTorch 2, PyTorch Lightning, TensorBoard, Git, JupyterLab}; training and inference done on ISATEC's remote compute servers.
\item Contact: Paul Lieutier --- \texttt{paul.lieutier@free.fr}
\end{zitemize}

\subsection{{Technical Consultant \hfill August 2022 --- June 2023}}
\subtext{FoxIntelligence \hfill Paris, France (remote)}
\begin{zitemize}
\item Led 7 e-commerce data analysis missions, improving product classification with \textbf{REGEX} and visualized results using \textbf{Tableau}, achieving over \textbf{80\% accuracy}, frequently reaching \textbf{100\%} in specific product categories.
\item Contact: Alexandre Sena --- \texttt{alexandre.sena@foxintelligence.fr}
\end{zitemize}

\subsection{{Robotics Engineer\hfill July 2021 --- January 2022}}
\subtext{Solystic \hfill Paris, France}
\begin{zitemize}
\item Developed an autonomous tracking system for the \textbf{Soly robot} to follow operators using \textbf{LIDAR} and computer vision, ensuring robust human-following in diverse indoor environments.
\item Validated solution successfully and approved for deployment by Solystic's R\&D leadership.
\item Stack: \textbf{Python 3, C, QtCreator, motion planning, LIDAR integration}.
\item Contact: Hicham El Bernoussi --- \texttt{hicham.el-bernoussi@solystic.com}
\end{zitemize}

\subsection{Teaching Experience}
\subtext{University of Chile}
\begin{zitemize}
\item Teaching assistant for the following courses: \textit{Probability and Statistics}, \textit{Introduction to Calculus}, \textit{Introduction to Algebra} \hfill 2019
\item Chemistry instructor in the Summer School organized by the University of Chile \hfill 2018
\end{zitemize}

%====================
% EXPERIENCE D
%====================
% \subsection{{ROLE / PROJECT D \hfill MMM YYYY --- MMM YYYY}}
% \subtext{company D \hfill somewhere, state}
% \begin{zitemize}
% \item Vestibulum accumsan massa quis dignissim faucibus.
% \item Maecenas suscipit mi ut ullamcorper pharetra.
% \item In vitae ligula tristique, iaculis tortor in, egestas magna.
% \item In fringilla purus malesuada lectus imperdiet pulvinar.
% \item Nulla eu dolor congue, mollis dui a, eleifend purus.
% \end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
