\cvsection{Publications}
\begin{itemize}
    \item \href{https://ieeexplore.ieee.org/document/10706460}{\textbf{Extended Target Tracking with 3D-INSEG and its Benefits in Dense Scenarios}}. Presented at \textit{FUSION 2024}. Explores a method to track multiple extended objects using stereo images and instance segmentation.
    
    \item \href{https://ieeexplore.ieee.org/document/10382343}{\textbf{3D-INSEG: A 3D Instance Segmentation Algorithm for Extended Object Tracking}}. Proposes a segmentation technique for detecting and tracking objects in 3D space using stereo images.
    
    \item \href{https://trilogia.utem.cl/articulos/structured-grammatical-evolution-for-modeling-the-multi-band-light-curves-of-supernova/}{\textbf{Structured Grammatical Evolution for Modeling the Multi-Band Light Curves of Supernova}}. Describes a symbolic regression method for modeling supernova behavior using structured evolutionary techniques.
\end{itemize}

\cvsection{Projects}

\cvsubsection{Transient Examples Generation using GANs}
\begin{itemize}
    \item Designed a GAN to generate synthetic images of transient astronomical objects (e.g., supernovae), augmenting the dataset and evaluating the impact on classification performance.
\end{itemize}

\cvsubsection{Dense Object Detection in Retail}
\begin{itemize}
    \item Developed an object detection model for supermarket shelves using mosaic-based data augmentation to outperform existing state-of-the-art architectures.
\end{itemize}

\cvsubsection{Smart Garage Door}
\begin{itemize}
    \item Built an Android-compatible system using ESP32 and proximity sensors to monitor garage door status in real-time.
\end{itemize}

\cvsubsection{Face Recognition for Celebrity Identification}
\begin{itemize}
    \item Collaborated with Prisma Media (France) to implement a system that identifies celebrities via facial recognition and provides related metadata.
\end{itemize}

\cvsubsection{Quora Insincere Questions Classifier}
\begin{itemize}
    \item Designed a text classification pipeline to detect malicious or insincere questions on the Quora platform using data mining and NLP techniques.
\end{itemize}

\cvsubsection{Indoor Positioning System with Wi-Fi}
\begin{itemize}
    \item Developed an indoor localization system using ESP32 devices to emit and measure Wi-Fi signals for estimating object positions.
\end{itemize}

\cvsection{Technical Skills}

{\LaTeXraggedright
\cvtag{Python}
\cvtag{PyTorch}
\cvtag{PyTorch Lightning}
\cvtag{TensorFlow}
\cvtag{scikit-learn}
\cvtag{Pandas}
\cvtag{scipy}
\cvtag{OpenCV}
\cvtag{C++}
\cvtag{Java}
\cvtag{Matlab}
\cvtag{ROS}
\cvtag{Android Studio}
\cvtag{Qt Creator}
\cvtag{Git}
\cvtag{Docker}
\cvtag{Anaconda}
\cvtag{SQL}
\cvtag{GCP}
\cvtag{Terraform}
\par}

\cvsection{Languages}
\begin{itemize}
    \item \textbf{Spanish}: Native
    \item \textbf{English}: C2 (Proficient)
    \item \textbf{French}: C2 (Proficient)
\end{itemize}
